Privacy-Preserving Localization Using Private Linear-Combination Aggregation

### 2021-05-27 main.tex
Rest of localisation section draft Still not happy with this and previous section - will get benjamin to look at it

\subsection{Localization} \label{subsec:localization}
As $h'_i$ and $\mat{H}'_{k,i}$ can be written as linear combinations of powers of location elements in $\vec{x}_{k|k-1}$, $\vec{i}_{k,i}$ and $\mat{I}_{k,i}$ can too.

After modifying measurements by . to produce modified measurement functions and Jacobians . and .,

With the existence of \eqref{eqn:modified_measurement_model}, measurement vector and measurement matrix linear combinations can be given in a similar form by
\begin{equation}
    \begin{split}
        \rvec{i}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \rv{r}_{k,i}^{-1}(\rv{z}'_{k,i} - h'_i(\rvec{x}_{k|k-1}) + \mat{H}'_{k,i}\rvec{x}_{k|k-1}) \\
        &= 
        \begin{bmatrix}
            \begin{split}
                &(2\rv{r}_{k,i}^{-1})\rv{x}_{k|k-1}^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_{k|k-1}\rv{y}_{k|k-1}^2 \\
                &\quad+ (-\rv{r}_{k,i}^{-1}s_{x,i})\rv{x}_{k|k-1}^2 + (-2\rv{r}_{k,i}^{-1}s_{x,i})\rv{y}_{k|k-1}^2 \\
                &\quad+ (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{x}_{k|k-1} + (-2\rv{r}_{k,i}^{-1}s_{x,i}^2)\rv{x}_{k|k-1}\\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{y,i}^2)\rv{x}_{k|k-1} + (2\rv{r}_{k,i}^{-1}s_{x,i}^3) \\
                &\quad+ (2\rv{r}_{k,i}^{-1}s_{x,i}s_{y,i}^2) + (-2\rv{r}_{k,i}^{-1}s_{x,i} \rv{z}'_{k,i})
            \end{split}
            \vspace{5pt}\\
            \begin{split}
                &(2\rv{r}_{k,i}^{-1})\rv{y}_{k|k-1}^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_{k|k-1}^2\rv{y}_{k|k-1} \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{y,i})\rv{x}_{k|k-1}^2 + (-2\rv{r}_{k,i}^{-1}s_{y,i})\rv{y}_{k|k-1}^2 \\
                &\quad+ (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{y}_{k|k-1} + (-2\rv{r}_{k,i}^{-1}s_{x,i}^2)\rv{y}_{k|k-1} \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{y,i}^2)\rv{y}_{k|k-1} + (2\rv{r}_{k,i}^{-1}s_{y,i}s_{x,i}^2) \\
                &\quad+ (2\rv{r}_{k,i}^{-1}s_{y,i}^3) + (-2\rv{r}_{k,i}^{-1}s_{y,i}\rv{z}'_{k,i})
            \end{split}
        \end{bmatrix}
    \end{split} \label{eqn:hrz_linear_comb}
\end{equation}
and
\begin{equation}
    \begin{split}
        \mat{I}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \rv{r}_{k,i}^{-1}\mat{H}'_{k,i} \\
        &=
        \begin{bmatrix}
            \beta_{11} & \beta_{12} \\
            \beta_{21} & \beta_{22}
        \end{bmatrix}\,,
    \end{split} \label{eqn:hrh_linear_comb}
\end{equation}
with
\begin{align*}
    \beta_{11} &= (4\rv{r}_{k,i}^{-1})\rv{x}_{k|k-1}^2 + (-8\rv{r}_{k,i}^{-1}s_{x,i})\rv{x}_{k|k-1} + (4\rv{r}_{k,i}^{-1}s_{x,i}^2)\,, \\
    \begin{split}
        \beta_{12} &= (4\rv{r}_{k,i}^{-1})\rv{x}_{k|k-1}\rv{y}_{k|k-1} + (-4\rv{r}_{k,i}^{-1}s_{y,i})\rv{x}_{k|k-1}  \\
        &\qquad+ (-4\rv{r}_{k,i}^{-1}s_{x,i})\rv{y}_{k|k-1} + (4\rv{r}_{k,i}^{-1}s_{x,i}s_{y,i})\,,
    \end{split}\\
    \beta_{21} &= \beta_{12}\,,\ \textrm{and} \\
    \beta_{22} &= (4\rv{r}_{k,i}^{-1})\rv{y}_{k|k-1}^2 + (-8\rv{r}_{k,i}^{-1}s_{y,i})\rv{y}_{k|k-1} + (4\rv{r}_{k,i}^{-1}s_{y,i}^2)\,.
\end{align*}
The above rearrangements result in $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ as linear comabinations of the weights 
\begin{equation}
    \begin{split}
        &\langle \rv{x}_{k|k-1}^3,\ \rv{y}_{k|k-1}^3,\ \rv{x}_{k|k-1}^2\rv{y}_{k|k-1},\ \rv{x}_{k|k-1}\rv{y}_{k|k-1}^2,\\
        &\quad \rv{x}_{k|k-1}^2,\ \rv{y}_{k|k-1}^2,\ \rv{x}_{k|k-1}\rv{y}_{k|k-1},\ \rv{x}_{k|k-1},\ \rv{y}_{k|k-1}\rangle\,,
    \end{split} \label{eqn:weights_to_broadcast}
\end{equation}
which again capture all the required information private to the navigator.

The final step required for the application of our LCAO secure encryption scheme to the linear combinations \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} is the handling of the scheme's instance variable $t$ in \eqref{eqn:our_scheme_lin_comb}. As six linear-combination aggregations occur at each time-step $k$ (four elements in $\mat{I}'_{k,i}$ and two in $\rvec{i}'_{k,i}$) and it is required for the security of the scheme that $t$ be unique for each aggregation at each time, this is handled by setting $t$ to the concatenation 
\begin{equation}
    t=k\mathbin\|v\mathbin\|w\mathbin\|\tau
\end{equation}
for aggregation in row $v$ and column $w$, with $\tau=0$ for aggregations in $\rvec{i}'_{k,i}$ and $\tau=1$ otherwise.
\begin{remark}
    The solutions \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} have been derived for two-dimensional localization, but can be similarly extended to the three-dimensional case. We note, however, the additional cost with increasing dimension. The number of weights is increased in the rearranged functions $h'_i$, and therefore combinatorially increased in $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ by . This results in a combinatorial increase in weights, and therefore communication, with respect to the number of state parameters required for computing functions $h_i$.
\end{remark}

@@

\subsection{Pseudocode} \label{subsec:pseudocode}
In this section, we piece together our LCAO secure encryption scheme in Section  with the modified measurement model in Sections  and  and define our privacy-preserving localization algorithm.

>>>>

\subsection{Localization} \label{subsec:localization}
Now that range measurements can be modified by \eqref{eqn:modified_measurement}, and the modified model \eqref{eqn:modified_measurement_model} can be used, corresponding modified measurement vectors $\vec{i}'_{k,i}$ and matrices $\mat{I}'_{k,i}$ can be computed as linear combinations of powers of location elements. This is given by
\begin{equation}
    \begin{split}
        \vec{i}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} r_{k,i}^{-1}(z'_{k,i} - h'_i(\vec{x}_{k|k-1}) + \mat{H}'_{k,i}\vec{x}_{k|k-1}) \\
        &= 
        \begin{bmatrix}
            \begin{split}
                &(2r_{k,i}^{-1})x_{k|k-1}^3 + (2r_{k,i}^{-1})x_{k|k-1}y_{k|k-1}^2 \\
                &\quad+ (-r_{k,i}^{-1}s_{x,i})x_{k|k-1}^2 + (-2r_{k,i}^{-1}s_{x,i})y_{k|k-1}^2 \\
                &\quad+ (2r_{k,i}^{-1}z'_{k,i})x_{k|k-1} + (-2r_{k,i}^{-1}s_{x,i}^2)x_{k|k-1}\\
                &\quad+ (-2r_{k,i}^{-1}s_{y,i}^2)x_{k|k-1} + (2r_{k,i}^{-1}s_{x,i}^3) \\
                &\quad+ (2r_{k,i}^{-1}s_{x,i}s_{y,i}^2) + (-2r_{k,i}^{-1}s_{x,i} z'_{k,i})
            \end{split}
            \vspace{5pt}\\
            \begin{split}
                &(2r_{k,i}^{-1})y_{k|k-1}^3 + (2r_{k,i}^{-1})x_{k|k-1}^2y_{k|k-1} \\
                &\quad+ (-2r_{k,i}^{-1}s_{y,i})x_{k|k-1}^2 + (-2r_{k,i}^{-1}s_{y,i})y_{k|k-1}^2 \\
                &\quad+ (2r_{k,i}^{-1}z'_{k,i})y_{k|k-1} + (-2r_{k,i}^{-1}s_{x,i}^2)y_{k|k-1} \\
                &\quad+ (-2r_{k,i}^{-1}s_{y,i}^2)y_{k|k-1} + (2r_{k,i}^{-1}s_{y,i}s_{x,i}^2) \\
                &\quad+ (2r_{k,i}^{-1}s_{y,i}^3) + (-2r_{k,i}^{-1}s_{y,i}z'_{k,i})
            \end{split}
        \end{bmatrix}
    \end{split} \label{eqn:hrz_linear_comb}
\end{equation}
and
\begin{equation}
    \begin{split}
        \mat{I}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} r_{k,i}^{-1}\mat{H}'_{k,i} \\
        &=
        \begin{bmatrix}
            \beta_{11} & \beta_{12} \\
            \beta_{21} & \beta_{22}
        \end{bmatrix}\,,
    \end{split} \label{eqn:hrh_linear_comb}
\end{equation}
with
\begin{align*}
    \beta_{11} &= (4r_{k,i}^{-1})x_{k|k-1}^2 + (-8r_{k,i}^{-1}s_{x,i})x_{k|k-1} + (4r_{k,i}^{-1}s_{x,i}^2)\,, \\
    \begin{split}
        \beta_{12} &= (4r_{k,i}^{-1})x_{k|k-1}y_{k|k-1} + (-4r_{k,i}^{-1}s_{y,i})x_{k|k-1}  \\
        &\qquad+ (-4r_{k,i}^{-1}s_{x,i})y_{k|k-1} + (4r_{k,i}^{-1}s_{x,i}s_{y,i})\,,
    \end{split}\\
    \beta_{21} &= \beta_{12}\,,\ \textrm{and} \\
    \beta_{22} &= (4r_{k,i}^{-1})y_{k|k-1}^2 + (-8r_{k,i}^{-1}s_{y,i})y_{k|k-1} + (4r_{k,i}^{-1}s_{y,i}^2)\,.
\end{align*}
The above rearrangements give $\vec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ as linear comabinations of
\begin{equation}
    \begin{split}
        &\{ x_{k|k-1}^3,\ y_{k|k-1}^3,\ x_{k|k-1}^2y_{k|k-1},\ x_{k|k-1}y_{k|k-1}^2,\\
        &\quad x_{k|k-1}^2,\ y_{k|k-1}^2,\ x_{k|k-1}y_{k|k-1},\ x_{k|k-1},\ y_{k|k-1}\}\,,
    \end{split} \label{eqn:weights_to_broadcast}
\end{equation}
which now capture all the private state information in $\vec{x}_{k|k-1}$ required at the sensors. The corresponding EIF update steps \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update} then become
\begin{equation}
    \vec{y}_{k|k} = \vec{y}_{k|k-1} + \sum^n_{i=1}\vec{i}'_{k,i} \label{eqn:eif_modified_vec_update}
\end{equation}
and
\begin{equation}
    \mat{Y}_{k|k} = \mat{Y}_{k|k-1} + \sum^n_{i=1}\mat{I}'_{k,i}\,, \label{eqn:eif_modified_mat_update}
\end{equation}
respectively. Additionally, we note the possible extension to the three-dimensional case.
\begin{remark}
    The above has been derived for two-dimensional localisation but can be similarly derived for three-dimensional case. However, we note that the number of weights increases combinatorially with the number of dimensions, thus affecting the cost of communication as well.
\end{remark}

The final step required for computing \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} at the sensors and \eqref{eqn:eif_modified_vec_update} and \eqref{eqn:eif_modified_mat_update} at the navigator using the proposed LCAO scheme, is handling the unique instance variables $t$ in the context of estimation timesteps $k$. This is done by elementwise linear combination of \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} and setting $t$ to the concatenation
\begin{equation}
    t=k\mathbin\|v\mathbin\|w\mathbin\|\tau
\end{equation}
for elements in row $v$ and column $w$, with $\tau=0$ for those in $\rvec{i}'_{k,i}$ and $\tau=1$ otherwise.

@@

\subsection{Pseudocode} \label{subsec:pseudocode}

Due to the complexity
several levels of computations
we summarise the privacy-preserving localisation filter in this section

In this section, we piece together our LCAO secure encryption scheme in Section  with the modified measurement model in Sections  and  and define our privacy-preserving localization algorithm.
